Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations

### 2020-09-08 paper/review/response-to-review.Rmd

Manuscript style comments:

o For the code layout in R publications, we typically distinguish input/output using Sinput/Soutput (or equivalently CodeInput/CodeOutput). Unless there are special reasons to format it differently, the input should use the text width (up to 76 or 77 characters) and be indented by two spaces, e.g.,

begin{Sinput}
R> example_model <- lm(response ~ variable1 + variable2 + variable3, 
+    weights = w, data = mydata)
\end{Sinput}

> I believe this has been resolved with the latest update to rticles.

@@

o The rule for capitalizing the starting letters of Figure, Section and Table is as follows: If you are referring to a particular figure/section/table then capitalize the first letter, otherwise use a lower-case first letter. For example, something shown in Section 4 vs. there are three sections in this paper.

> Appropriate instances of `section` and `figure` have been replaced with `Section` and `Figure`.

o All captions should appear below the corresponding figure/table. The captions should be in sentence style and end with a period.  No additional formatting (such as \emph, f or \it) should be used for the caption.

> Captions are below every figure, and for each table these will be moved manually in the LaTeX output.

@@

o All table row/column headers should also be in sentence style. There should not be further footnote-style annotations in tables; these should all be placed in the caption.

> Need to double check about headings here for tables - Di should I change things like "n_miss" to "Num. Missing" ?

### 2020-09-08 paper/tidy-missing-data-paper.Rmd
finish reviewer comments draft

```{r warning, fig.cap = "How ggplot2 behaves when displaying missing values. A warning message is displayed, but missing values are not shown in the plot", fig.height = 4, fig.width = 8, out.width = "75%", warning = FALSE, fig.show = 'hold'}
p1 <- ggplot(oceanbuoys,
       aes(x = humidity,
           y = air_temp_c)) +
  geom_point(size = 0.5) +
  theme(aspect.ratio = 1) + 
  labs(x = "Humidity",
       y = "Air Temperature (C)")

@@

### The tidyverse {#the-tidyverse}

@@

```{r parallel-cord-plot, fig.width = 8, fig.height = 4, out.width = "100%", echo = FALSE, fig.cap = "Parallel coordinate plot shows missing values imputed 10\\% below range for the oceanbuoys dataset. Values are colored by missingness of humidity. Humidity is missing for low air and sea temperatures, and is missing for one year and one location. "}

@@

```{r tidy-coefs, fig.height = 2, fig.width = 7, fig.cap = "The coefficient estimate for the number of rooms varies according to the imputed dataset. Complete case dataset produced lower coefficients, compared to imputed datasets", out.width = "100%"}

>>>>

```{r warning, fig.cap = "How ggplot2 behaves when displaying missing values. A warning message is displayed, but missing values are not shown in the plot.", fig.height = 4, fig.width = 8, out.width = "75%", warning = FALSE, fig.show = 'hold'}
p1 <- ggplot(oceanbuoys,
       aes(x = humidity,
           y = air_temp_c)) +
  geom_point(size = 0.5) +
  theme(aspect.ratio = 1) + 
  labs(x = "Humidity",
       y = "Air Temperature (C)")

@@

### The \pkg{tidyverse} {#the-tidyverse}

@@

```{r parallel-cord-plot, fig.width = 8, fig.height = 4, out.width = "100%", echo = FALSE, fig.cap = "Parallel coordinate plot shows missing values imputed 10\\% below range for the oceanbuoys dataset. Values are colored by missingness of humidity. Humidity is missing for low air and sea temperatures, and is missing for one year and one location."}

@@

```{r tidy-coefs, fig.height = 2, fig.width = 7, fig.cap = "The coefficient estimate for the number of rooms varies according to the imputed dataset. Complete case dataset produced lower coefficients, compared to imputed datasets.", out.width = "100%"}
